Random Forests", OAs

### 2025-02-05 src/oa_RF_corrected_10.Rmd
oa_10

# Random Forest 
# 
# 3716736 samples
#       8 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 3215700, 2574600, 3128916, 3225315, 2789175, 2618196, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE      Rsquared   MAE     
#   2     variance    21.61442  0.4482161  6.736518
#   2     extratrees  23.82034  0.3557068  6.584642
#   5     variance    21.58205  0.4549608  6.845549
#   5     extratrees  23.00958  0.3848122  6.884375
#   8     variance    22.07397  0.4426922  6.949996
#   8     extratrees  23.17989  0.3796106  7.060913
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 5, splitrule
#  = variance and min.node.size = 5.

>>>>

# Random Forest 
# 
# 3716736 samples
#       8 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 3215700, 2574600, 3128916, 3225315, 2789175, 2618196, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE      Rsquared   MAE     
#   2     variance    21.61233  0.4487783  6.733987
#   2     extratrees  23.80635  0.3564440  6.583231
#   5     variance    21.59062  0.4546951  6.845095
#   5     extratrees  23.00905  0.3846503  6.885083
#   8     variance    22.10042  0.4421229  6.953833
#   8     extratrees  23.19776  0.3791247  7.061227
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 5, splitrule = variance and
#  min.node.size = 5.
